Blockchain in the Industrial Sector

### 2020-06-01 paper.tex
Add DID and VC to Proposed Solution Add DID and VC to Implementation section

\section{Proposed Solution}
To answer the research questions, we will try to build a blockchain-based system in the area of manufacturing. The system collects, stores, and manages the key information generated by the factory infrastructure. The focus is on both the machines and the products being manufactured. Regarding the products, the system provides the ability to track and trace each product throughout a production pipeline. Regarding the machines, it tracks the status of the machines at any point in time. The system enables also the autonomous machine-to-machine communications. Where one machine can ask another machine to perform a certain task without any human involvement. The system envisioned will be designed and implemented using blockchain technologies such as smart contracts. It will be decentralized and distributed. The system will be serving the entities participating in the manufacturing industry such as suppliers, manufacturers, and customers.

@@

\noindent In the system, each machine and product has a digital profile. This profile represents the digital twin of the machine or the product.  The profile of the product contains all related information about how the product has been manufactured. The profile will contain the full log of all the industrial tasks performed to this product. This includes information about the machines performed the tasks and information about the surrounding environment. The profile of the machine will contain related information about the industrial tasks performed by this machine and information about the communication with other machines. All the data in the network is stored on a blockchain and is available to anyone running the system software with correct authentication.

\noindent
To manage the identity of the machines and the products, each digital twin will have a decentralized identifier (DID) \footnote{https://www.w3.org/TR/did-core/}. DID is one new generation of identifiers supporting self-sovereign identity \cite{Bartolomeu2019}. DID will link the physical object (product/machine) with its virtual twin on the network. This DID will be registered within the blockchain which means no centralized registration authority is required. Each DID point to DID documents (DDOs) contains some key information about the object such as (proof purposes, verification methods, and service endpoints).

@@

@@

>>>>

\section{Proposed Solution}
To answer the research questions, we will build a blockchain-based system in the area of manufacturing. The system collects, stores, and manages the key information generated by the factory infrastructure. The focus is on both the machines and the products being manufactured. Regarding the products, the system provides the ability to track and trace each product throughout a production pipeline. Regarding the machines, it tracks the status of the machines at any point in time. The system enables also the autonomous machine-to-machine communications. Where one machine can ask another machine to perform a certain task without any human involvement. The system envisioned will be designed and implemented using blockchain technologies and smart contracts. It will be decentralized and distributed to serve the entities participating in the manufacturing industry such as suppliers, manufacturers, and customers.

@@

\noindent In the system, each machine and product has a digital profile. This profile represents the digital twin of the machine or the product.  The profile of the product contains all related information about how the product has been manufactured. The profile will contain the full log of all the industrial tasks performed to this product. This includes information about the machines performed the tasks and information about the surrounding environment. The profile of the machine will contain related information about the industrial tasks performed by this machine and information about the communication with other machines. All the data in the network is stored on a blockchain and is available to anyone running the system software with correct authentication.
\bigbreak

\noindent
We are using a blockchain-based approach to manage the identity of all the entities of the system. This includes products, machines, and users. It is a self-sovereign approach where the access control rights and management of identities are under the control of identity owners. The approach is based on the emerging standard from the World Wide Web Consortia (W3C) Decentralized Identifiers (DIDs) \footnote{https://www.w3.org/TR/did-core/}. To manage the identity of the machines and the products, each digital twin will have a DID. It is one new generation of identifiers supporting self-sovereign identity \cite{Bartolomeu2019}. DID will link the physical object (product/machine) with its virtual twin on the network. This DID will be registered within the blockchain which means no centralized registration authority is required. Each DID point to DID documents (DDOs) contains some key information about the object such as (proof purposes, verification methods, and service endpoints).
\bigbreak

\noindent
To establish trust and maintaining secure relationships between the machines while communication, the system is using another standard from W3C which is Verifiable Credentials (VC) \footnote{https://www.w3.org/TR/vc-data-model/} to represent the capabilities and the specification of each machine. A verifiable credential is a tamper-resistant credential that is cryptographically signed by its issuer. This allows one machine to verify the ability of another machine to deliver a certain service. Using verifiable credentials in our system is not limited to machines, the products also have verifiable credentials. Such credentials can be used to prove that the products meet quality standards. This allows the customers who purchase the products to check if the products are compliant to a certain quality certificate or standard.

@@

\subsection{Identities Management}
We mentioned earlier that identity management will be based on the W3C DID standard. The W3C only published a specification of DID and it is up to the implementer to specify the used technologies and the technical details to implement the specification. Currently, there are around 40 experimental implementations \footnote{https://w3c-ccg.github.io/did-method-registry/} of the DID specification. For our implementation, we chose an ERC-1056 \footnote{https://github.com/uport-project/ethr-did}. It is an open-source lightweight implementation developed by uPort \footnote{https://www.uport.me/}. It consists of one smart contract that acts as a global registry for storing and managing all identifiers. ERC-1056 describing an identity system for Ethereum and it is compliant with the DID standard. The blockchain of our system will have a deployed copy of the ERC-1056 smart contract. All the identity management operations will be done in the form of transactions through this contract.

\subsection{Verifiable Credentials}
The verifiable credential in our system is based on the Verifiable Credentials Data Model published by W3C. The system is using off-chain credentials written as JSON Web Tokens (JWT). The same library used for identity management will also be used to verify and sign the credentials.

@@

\section{Work Plan}
As we saw in the high-level architecture the system is consists of two main parts. The blockchain and smart contracts part and the factory infrastructure part. We consider each part of a work package. The first work package involves the main task which is modeling the system. Another task is writing smart contracts. Setting up the blockchain and the MQTT broker are also tasks in this package. The second package involves work regarding controlling the factory model. The factory model comes with a predefined manufacturing scenario. This has to be changed to adopt the concept of machine-to-machine communication. This third work package is developing the front-end web application. This involves tasks like developing the user interfaces and writing the JavaScript code which will connect the interface with the blockchain. \noindent The figure \ref{fig:time_plan} shows a high-level time plan.

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figures/time_plan.jpeg}
\caption{Estimated Time Plan}
\label{fig:time_plan}
\end{figure}
